### 2022-03-02 manuscript.tex
Include all references within a single \cite{}

A probabilistic forecast is a forecast to which probabilities are assigned to 
various possible outcomes. There are a number of ways the probabilities or 
uncertainty may be represented. A common representation is either a continuous 
or
discrete parametric distribution function (a pdf or pmf). Much of the literature 
on calibration, sharpness and scoring of a forecast pertains to parametric 
distribution forecasts (see for example 
\cite{gneiting2007probabilistic},
\cite{gneiting2013combining} \cite{baran2018combining}).
Other common representations include samples \cite{krueger2016probabilistic}, 
discretized bins 
and quantile or interval type forecasts \cite{taylor2021evaluating} 
\cite{bracher2021evaluating}. Each representation may be more or less 
appropriate than the others for a given problem but knowing how to interpret, 
score and contruct ensemble forecasts for a selected representation is a must 
when multiple forecasts of the same event are involved.

>>>>

A probabilistic forecast is a forecast to which probabilities are assigned to 
various possible outcomes. There are a number of ways the probabilities or 
uncertainty may be represented. A common representation is either a continuous 
or
discrete parametric distribution function (a pdf or pmf). Much of the literature 
on calibration, sharpness and scoring of a forecast pertains to parametric 
distribution forecasts
\cite[see, e.g.]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}).
Other common representations include samples \cite{krueger2016probabilistic}, 
discretized bins 
and quantile or interval type forecasts \cite{taylor2021evaluating} 
\cite{bracher2021evaluating}. Each representation may be more or less 
appropriate than the others for a given problem but knowing how to interpret, 
score and contruct ensemble forecasts for a selected representation is a must 
when multiple forecasts of the same event are involved.
